### 2018-04-27 doc/paper.tex
Updating some notation.
- Switching out `e_j` for `\Delta b_j` (I want to refer to
  the higher order errors in similar ways)
- Dropping `p` for a bold `b` when referring to the polynomial
  in functions
- Dropping usage of `p_j` as Bernstein coefficients
- Changing Bernstein notation from lowercase (`b_{j, n}`) to
  uppercase (`B_{j, n}`)

  \begin{algorithmic}
    \Function{\(\mathtt{res} = \mathtt{DeCasteljau}\)}{$p, s$}
      \State \(n = \texttt{length}(p) - 1\)
      \State \(r = 1 \ominus s\)
      \\
      \For{\(j = 0, \ldots, n\)}
        \State \(b_j^{(n)} = p_j\)
      \EndFor
      \\
      \For{\(k = n - 1, \ldots, 0\)}
        \For{\(j = 0, \ldots, k\)}
          \State \(b_j^{(k)} = \left(r \otimes b_j^{(k + 1)}\right) \oplus
              \left(s \otimes b_{j + 1}^{(k + 1)}\right)\)
        \EndFor
      \EndFor
      \\
      \State \(\mathtt{res} = b_0^{(0)}\)
    \EndFunction
  \end{algorithmic}
\end{algorithm}

@@

  \begin{algorithmic}
    \Function{\(\mathtt{res} = \mathtt{CompDeCasteljau}\)}{$p, s$}
      \State \(n = \texttt{length}(p) - 1\)
      \State \(\left[r, \rho\right] = \mathtt{TwoSum}(1, -s)\)
      \\
      \For{\(j = 0, \ldots, n\)}
        \State \(b_j^{(n)} = p_j\)
        \State \(e_j^{(n)} = 0\)
      \EndFor
      \\
      \For{\(k = n - 1, \ldots, 0\)}
        \For{\(j = 0, \ldots, k\)}
          \State \(\left[P_1, \pi_1\right] = \mathtt{TwoProd}\left(
              r, b_j^{(k + 1)}\right)\)
          \State \(\left[P_2, \pi_2\right] = \mathtt{TwoProd}\left(
              s, b_{j + 1}^{(k + 1)}\right)\)
          \State \(\left[b_j^{(k)}, \sigma_3\right] = \mathtt{TwoSum}(
              P_1, P_2)\)
          \State \(w = \pi_1 \oplus \pi_2 \oplus \sigma_3 \oplus
              \left(\rho \otimes b_j^{(k + 1)}\right)\)
          \State \(e_j^{(k)} = w \oplus \left(s \otimes e_{j + 1}^{(k + 1)}
              \right) \oplus \left(r \otimes e_j^{(k + 1)}\right)\)
        \EndFor
      \EndFor
      \\
      \State \(\mathtt{res} = b_0^{(0)} \oplus e_0^{(0)}\)
    \EndFunction
  \end{algorithmic}
\end{algorithm}

@@

Consider de Casteljau's method to evaluate a degree \(n\)
polynomial in Bernstein-B\'{e}zier form with control points \(p_j\):
\begin{align*}
    b_j^{(n)} &= p_j \\
    b_j^{(k)} &= (1 - s) b_j^{(k + 1)} + s b_{j + 1}^{(k + 1)} \\
    b(s) &= b_0^{(0)}.
\end{align*}

@@

For a polynomial \(p(s)\) in Bernstein form, we have (\cite{Jiang2010}):
\[\cond{p(s)} = \frac{\widetilde{p}\left(s\right)}{
  \left|p(s)\right|} = \frac{\sum_j \left|p_j\right| \left|b_{j, n}(s)\right|}{
  \left|p(s)\right|}.\]
The Bernstein form is suited for \(s \in \left[0, 1\right]\), which means
\(b_{j, n}(s) \geq 0\) typically. If \(s \in \left[0, 1\right]\) and each
\(p_j \geq 0\) we must necessarily have \(\cond{p(s)} = 1\). To see an
example in use, consider
\[p(s) = (1 - 2s)^n = \left[(1 - s) - s\right]^n = \sum_j \binom{n}{j}
(1 - s)^{n - j} (-s)^j = \sum_j (-1)^j b_{j, n}(s)\]
and input values of the form \(x = \frac{1}{2} + \delta\)
(with \(\left|\delta\right| \ll \frac{1}{2}\)). Since \(p_j = (-1)^j\)
we have \(\widetilde{p}(s) = \left[(1 - s) + s\right]^n = 1\)
\[\cond{p\left(\frac{1}{2} + \delta\right)} = \frac{1}{
  \left|2\delta\right|^n}.\]
As \(\delta \to 0\), this value approaches \(\infty\) (as expected).

@@

Consider
\[p(s) = (4s - 3)^3 (8s + 7) = (-189) b_{0, 4}(s) + (-54) b_{1, 4}(s) +
57 b_{2, 4}(s) + (-32) b_{3, 4}(s) + 15 b_{4, 4}(s)\]
at the point \(s = \frac{3}{4} + 800 u\). In exact arithmetic, we
have \(p(s) = 2^{38.6} u^3 + \mathcal{O}\left(u^4\right)\).
However, using the compensated de Casteljau algorithm results in
\(\widehat{p} + \widehat{e} = 0\):

\begin{center}
  \begin{tabular}{>{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$}}
    \toprule
    k & j & b_j^{(k)} & e_j^{(k)} \\
    \midrule
    3 & 0 & -87\frac{3}{4} + 108032u & -32u \\
    3 & 1 & 29\frac{1}{4} + 88768u & 32u \\
    3 & 2 & -9\frac{3}{4} - 71200u & 0 \\
    3 & 3 & 3\frac{1}{4} + 37600u & 0 \\
    \midrule
    2 & 0 & 187200u & -15360000u^2 \\
    2 & 1 & -62408u & 8u - 128000000u^2 \\
    2 & 2 & 20800u & 87040000u^2 \\
    \midrule
    1 & 0 & -6u - 199688192u^2 & \boxed{6u - 99831808u^2} \\
    1 & 1 & -2u + 66568192u^2  & \boxed{2u + 33271808u^2} \\
    \midrule
    0 & 0 & -3u + 7296u^2 & \boxed{3u - 7296u^2} \\
    \bottomrule
  \end{tabular}
\end{center}
This is due to dropped terms: \(e_0^{(1)}\) drops \(-90112000000u^3\),
\(e_1^{(1)}\) drops \(172032000000u^3\), \(e_0^{(0)}\) drops
\(319488000000u^3\) (that's relative to the \textbf{incorrect} \(e_j^{(1)}\)
terms, if compared to the correct terms there'd also be a \(u^4\) term
dropped).

>>>>

  \begin{algorithmic}
    \Function{\(\mathtt{res} = \mathtt{DeCasteljau}\)}{$\mathbf{b}, s$}
      \State \(n = \texttt{length}(b) - 1\)
      \State \(r = 1 \ominus s\)
      \\
      \For{\(j = 0, \ldots, n\)}
        \State \(b_j^{(n)} = b_j\)
      \EndFor
      \\
      \For{\(k = n - 1, \ldots, 0\)}
        \For{\(j = 0, \ldots, k\)}
          \State \(b_j^{(k)} = \left(r \otimes b_j^{(k + 1)}\right) \oplus
              \left(s \otimes b_{j + 1}^{(k + 1)}\right)\)
        \EndFor
      \EndFor
      \\
      \State \(\mathtt{res} = b_0^{(0)}\)
    \EndFunction
  \end{algorithmic}
\end{algorithm}

@@

  \begin{algorithmic}
    \Function{\(\mathtt{res} = \mathtt{CompDeCasteljau}\)}{$\mathbf{b}, s$}
      \State \(n = \texttt{length}(\mathbf{b}) - 1\)
      \State \(\left[r, \rho\right] = \mathtt{TwoSum}(1, -s)\)
      \\
      \For{\(j = 0, \ldots, n\)}
        \State \(b_j^{(n)} = b_j\)
        \State \(\Delta b_j^{(n)} = 0\)
      \EndFor
      \\
      \For{\(k = n - 1, \ldots, 0\)}
        \For{\(j = 0, \ldots, k\)}
          \State \(\left[P_1, \pi_1\right] = \mathtt{TwoProd}\left(
              r, b_j^{(k + 1)}\right)\)
          \State \(\left[P_2, \pi_2\right] = \mathtt{TwoProd}\left(
              s, b_{j + 1}^{(k + 1)}\right)\)
          \State \(\left[b_j^{(k)}, \sigma_3\right] = \mathtt{TwoSum}(
              P_1, P_2)\)
          \State \(w = \pi_1 \oplus \pi_2 \oplus \sigma_3 \oplus
              \left(\rho \otimes b_j^{(k + 1)}\right)\)
          \State \(\Delta b_j^{(k)} = w \oplus \left(s \otimes
              \Delta b_{j + 1}^{(k + 1)}
              \right) \oplus \left(r \otimes \Delta b_j^{(k + 1)}\right)\)
        \EndFor
      \EndFor
      \\
      \State \(\mathtt{res} = b_0^{(0)} \oplus \Delta b_0^{(0)}\)
    \EndFunction
  \end{algorithmic}
\end{algorithm}

@@

Consider de Casteljau's method to evaluate a degree \(n\)
polynomial in Bernstein-B\'{e}zier form with control points \(b_j\):
\begin{align*}
    b_j^{(n)} &= b_j \\
    b_j^{(k)} &= (1 - s) b_j^{(k + 1)} + s b_{j + 1}^{(k + 1)} \\
    b(s) &= b_0^{(0)}.
\end{align*}

@@

For a polynomial \(p(s)\) in Bernstein form, we have (\cite{Jiang2010}):
\[\cond{p(s)} = \frac{\widetilde{p}\left(s\right)}{
  \left|p(s)\right|} = \frac{\sum_j \left|b_j\right| \left|B_{j, n}(s)\right|}{
  \left|p(s)\right|}.\]
The Bernstein form is suited for \(s \in \left[0, 1\right]\), which means
\(B_{j, n}(s) \geq 0\) typically. If \(s \in \left[0, 1\right]\) and each
\(b_j \geq 0\) we must necessarily have \(\cond{p(s)} = 1\). To see an
example in use, consider
\[p(s) = (1 - 2s)^n = \left[(1 - s) - s\right]^n = \sum_j \binom{n}{j}
(1 - s)^{n - j} (-s)^j = \sum_j (-1)^j B_{j, n}(s)\]
and input values of the form \(x = \frac{1}{2} + \delta\)
(with \(\left|\delta\right| \ll \frac{1}{2}\)). Since \(b_j = (-1)^j\)
we have \(\widetilde{p}(s) = \left[(1 - s) + s\right]^n = 1\)
\[\cond{p\left(\frac{1}{2} + \delta\right)} = \frac{1}{
  \left|2\delta\right|^n}.\]
As \(\delta \to 0\), this value approaches \(\infty\) (as expected).

@@

Consider
\[p(s) = (4s - 3)^3 (8s + 7) = (-189) B_{0, 4}(s) + (-54) B_{1, 4}(s) +
57 B_{2, 4}(s) + (-32) B_{3, 4}(s) + 15 B_{4, 4}(s)\]
at the point \(s = \frac{3}{4} + 800 u\). In exact arithmetic, we
have \(p(s) = 2^{38.6} u^3 + \mathcal{O}\left(u^4\right)\).
However, using the compensated de Casteljau algorithm results in
\(b_0^{(0)} + \Delta b_0^{(0)} = 0\):

\begin{center}
  \begin{tabular}{>{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$}}
    \toprule
    k & j & b_j^{(k)} & \Delta b_j^{(k)} \\
    \midrule
    3 & 0 & -87\frac{3}{4} + 108032u & -32u \\
    3 & 1 & 29\frac{1}{4} + 88768u & 32u \\
    3 & 2 & -9\frac{3}{4} - 71200u & 0 \\
    3 & 3 & 3\frac{1}{4} + 37600u & 0 \\
    \midrule
    2 & 0 & 187200u & -15360000u^2 \\
    2 & 1 & -62408u & 8u - 128000000u^2 \\
    2 & 2 & 20800u & 87040000u^2 \\
    \midrule
    1 & 0 & -6u - 199688192u^2 & \boxed{6u - 99831808u^2} \\
    1 & 1 & -2u + 66568192u^2  & \boxed{2u + 33271808u^2} \\
    \midrule
    0 & 0 & -3u + 7296u^2 & \boxed{3u - 7296u^2} \\
    \bottomrule
  \end{tabular}
\end{center}
This is due to dropped terms: \(\Delta b_0^{(1)}\) drops \(-90112000000u^3\),
\(\Delta b_1^{(1)}\) drops \(172032000000u^3\), \(\Delta b_0^{(0)}\) drops
\(319488000000u^3\) (that's relative to the \textbf{incorrect}
\(\Delta b_j^{(1)}\) terms, if compared to the correct terms there'd also
be a \(u^4\) term dropped).
